%\section{Appendix}
%\label{sec:Appendix}
\begin{appendices}
%\appendixname{Appendix}
%\appendix
\textbf{A. SCREENING QUESTIONNAIRE}
\\
Thank you for your interest in participating in our study on Online Communication Practices.   Please fill out this brief 1-minute questionnaire regarding yourself and your online communication choices. We will utilize your answers to determine if you are eligible to participate in the study. If you qualify, we will contact you via email for a 30-45 minute in-person/ video conference/ telephone interview for which you will receive $10 cash/$10 Amazon gift certificate as a token of our appreciation for your participation. If you do not qualify for participation, your responses will be safely discarded. 
\begin{enumerate}
\item What is your Year of Birth?
\item Which Gender do you identify with the most?
\begin{itemize}
\item Female
\item Male
\item Other- Please Specify:
\item Do not wish to specify
\end{itemize}
\item Are you affiliated with ANONYMOUS University?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item (If affiliated with ANONYMOUS University) What is your affiliation with ANONYMOUS University? (Check all that apply.)
\begin{itemize}
\item Undergraduate Student
\item Graduate Student
\item Faculty
\item Staff
\item Retired
\item Other - Please Specify:
\end{itemize}
\item How long have you been living in the US?
\begin{itemize}
\item Less than a year
\item 1 year
\item 2 years
\item 3 years
\item 4 years
\item 5 years
\item 6 years
\item 7 years
\item 8 years
\item 9 years
\item 10 years
\item 11 years
\item 12 years
\item 13 years
\item 14 years
\item 15 years
\item 16 years
\item 17 years
\item 18 years
\item 19 years
\item 20 years
\item More than 20 years
\end{itemize}
\item Do you have a Facebook account?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item (If Yes to Facebook account) What do you use Facebook for? (Check all that apply.)
\begin{itemize}
\item Posting Status Updates, Pictures, Videos, etc.
\item Reading the News Feed.
\item Commenting on Others' Posts.
\item Liking Others' Posts.
\item Messaging Facebook Friends.
\item Other - Please Specify:
\end{itemize}

\item (If Yes to Facebook account) Compared to a year ago, how often do you post on Facebook?
\begin{itemize}
\item More often than a year ago.
\item About the same amount as a year ago.
\item Less often than a year ago.
\end{itemize}
\item (If Yes to Facebook account) How would you characterize your use of Facebook?
\begin{itemize}
\item I write/post/produce more than I read/click/consume.
\item I read/click/consume more than I write/post/produce.
\item I write/post/produce roughly the same amount as I read/click/consume.
\item Please elaborate:
\end{itemize}
\item If you qualify for the study, which email address should we use to contact you for scheduling an in-person/ video conference/ telephone interview?
\item (If not affiliated with ANONYMOUS University) How would you prefer to be interviewed?
\begin{itemize}
\item Video Conference
\item Telephone Interview
\end{itemize}
\end{enumerate}
\textbf{B. SEMI-STRUCTURED INTERVIEW QUESTIONS}
\textbf{\textit{Social media accounts}}
\begin{enumerate}
\item Do you currently have a Facebook account you actively use?
\item What other social media platforms do you use?
\item Do you use your Facebook account to login to other services on the Internet? Why or why not?
\end{enumerate}
\textbf{\textit{If participant does not have a Facebook account}}
\begin{enumerate}
\item Did you ever have a Facebook account?
\item If Yes, why did you choose to get rid of the Facebook account?
\item If No, why did you choose not to create a Facebook account?
\item If No, is there anything that would prompt you to create a Facebook account in future?
\item If No, what do you believe you are gaining or missing by not having a Facebook account?
\end{enumerate}
\textbf{\textit{If participant has a Facebook Account}}
\begin{enumerate}
\item What prompted you to create a Facebook account?
\item How long have you had a Facebook account?
\item Why do you use Facebook?
\item What aspects of using Facebook do you like?
\item What aspects of using Facebook do you dislike?
\item Which features of Facebook do you typically use (i.e., chat, groups, events, etc.)? Why?
\item How often do you post on Facebook?
\item What do you post?
\item How has your posting on Facebook changed over time?
\item If reduced or increased, was the change abrupt or gradual? Why?
\item If reduced or increased, how is it related to changes in Facebook?
\item If reduced or increased, how is it related to changes in your own life and views?
\item In what ways is Facebook satisfying to use?
\item In what ways is Facebook dissatisfying to use?
\item In what ways is Facebook useful or productive?
\item In what ways is Facebook not useful or unproductive?
\item What role does Facebook play in your life?
\end{enumerate}
\textbf{\textit{Facebook Behavior}}
\begin{enumerate}
\item What do you think people think of you based on your Facebook profile?
\item How do you decide what you post on Facebook?
\item How do you manage how Facebook makes you look to others?
\item How do you decide what to include or leave out in your posts?
\item Have you ever posted anything that you later edited or deleted?
\item If yes, why did you edit or delete it?
\item Have you ever regretted a post after you made it? If yes, why? What did you do about the regret?
\item In what ways are you a producer of information on Facebook?
\item In what ways are you a consumer of information on Facebook?
\item Which of the two modes (producer and consumer) is your predominant or preferred way of using Facebook? Why? 
\end{enumerate}
\textbf{\textit{Facebook Privacy}}
\begin{enumerate}
\item In what ways is your use of Facebook “public”?
\item In what ways is your use of Facebook “private” or restricted?
\item What are your privacy settings on Facebook? (public, friends only, only me, others)
\item Why did you choose these settings?
\item When do you change your privacy settings? How often?
\item Do you restrict yourself from being seen on Facebook? If yes, in what way?
\item Have you ever unfriended or blocked your friends on Facebook? If yes, why?
\item What do you believe Facebook uses your data for?
\item What do you think about Facebook’s policies regarding the use of your Facebook data?
\item What do you feel about sharing data and information on Facebook?
\end{enumerate}
\textbf{\textit{Abandoning Facebook/Returning to Facebook}}
\begin{enumerate}
\item Do you ever feel like leaving Facebook entirely (deleting your account)? If yes, why? If no, what about curtailing or restricting your Facebook use? If yes, why and in what ways?
\item If you delete/deactivate your Facebook account, which other systems would you switch to? Why?
\item Do you know anyone who has deactivated their Facebook account or stopped or reduced use of Facebook? If yes, why did they do so?
\item Have you ever deactivated your Facebook account? If yes, why? Did you reactivated it later? If yes, why?
\end{enumerate}
\textbf{\textit{Demographic Questions}}
\begin{enumerate}
\item Where did you grow up?
\item What do you do?
\item If you study, what is your major?
\end{enumerate}
\textbf{\textit{Ending Question}}
\begin{enumerate}
\item Is there anything else regarding your Facebook usage that you would like to share with us?
\end{enumerate}
\end{appendices}